Article Title

### 2013-10-01 sections/Estimators.tex
completed estimator description.

The target estimate is then 
\begin{equation}
\hat T_d = \hat L_d\hat L_d^\T + \hat \Psi
\end{equation}
where $\hat L_d$ is the $p\times d$ \emph{loading matrix} and $\hat \Psi$ is the $p\times p$ diagonal matrix of specific variances. The value of $\hat T\_d$ is found by minimizing $\loss{\hat T_d, \hat\Sigma_0}$.

@@

\subsubsection*{Estimator C: Spare inverse}
\emph{Estimator C} produces a low-dimensional estimate by finding an approximation of $\hat\Sigma_0$ that has many zeros in its inverse. This approximation problem is known as \emph{covariance selection} \cite{Dempster:1972,Meinshausen:2006}.

For Gaussian Graphical Models, zeros in the inverse covariance matrix indicate statisitcal independence between the corresponding pairs. Thus the inverse covariance matrix is also the adjacency matrix of the graphical model, indicating which pairs are conditionally dependent. \TODO{discuss how quickly (or slowly) this breaks down with deviations from gaussianity, e.g.~MaxEnt models, Ising models.} \TODO{Also, motivate this from the perpsective of linear regression as in \cite{Varoquaux:2012}.} \TODO{Relate to partial pairwise correlations.} Regularization of covariance matrix estimation by sparsifying the inverse of the estimate has been using in function genomics \cite{Schafer:2005,other} and fMRI functional connectivity \cite{Varoquaux:2012}.

The covariance matrix estimate is then 
\begin{equation}
\hat\Sigma_\rho = \left(\arg\min\limits_S \loss{S^{-1},\hat\Sigma_0}  \right)^{-1} \quad \mbox{such that} \quad  \|S_\rho\|_0 = \rho
\end{equation}
where $S_\rho$ is a sparse matrix with $\rho$ non-zero coefficients. $\|S\|_0$ denotes the number of non-zero elements of matrix $S$.
Solving this approximation in this form is computationally challenging. However, replacing the $L_0$ norm with the $L_1$ norm makes the approximation problem convex  while still allowing to uncover the true zero structure \cite{Friedman:2008,Donoho:2000}.  The resulting algorithm, known as \emph{graphical lasso} \cite{Friedman:2008} finds the estimator as 
\begin{equation}
\hat\Sigma_\lambda = \left(\arg\min\limits_S \loss{S^{-1},\hat\Sigma_0} + \lambda \|S\|_1\right)^{-1}
\end{equation}
where $\lambda \|S\|_1$ is the $L_1$ norm of the matrix. \TODO{clarify}.

@@

In estimate D, the target $\hat R_{d,\alpha}$ is the matrix whose inverse is the sum of a sparse matrix $\hat S_\alpha$ and a low-rank matrix $\hat L_d$ of rank $d$.
\begin{equation}
\hat R_{d,\alpha} = (\hat S_\alpha + \hat L_d)^{-1}
\end{equation}

If all dependencies are linear, the estimate D describes a group of neurons where each interacts with a small number of latent units and a small fraction of the observed neurons.

\cite{Ma:2013}

>>>>

The target estimate is then 
\begin{equation}
\hat T_d = \hat L_d + \hat \Psi
\end{equation}
where $\hat L_d$ is a $p\times p$ matrix of rank $d$ and $\hat \Psi$ is a $p\times p$ diagonal matrix. The value of $\hat T_d$ is found by minimizing $\loss{\hat T_d, \hat\Sigma_0}$.

@@

\subsubsection*{Estimator C: Spare inverse}
\emph{Estimator C} produces a low-dimensional estimate by finding an approximation of $\hat\Sigma_0$ that has many zeros in its inverse. This approximation problem is known as \emph{covariance selection} \cite{Dempster:1972}.

For Gaussian Graphical Models, zeros in the inverse covariance matrix indicate statisitcal independence between the corresponding pairs. Thus the inverse covariance matrix $S=-\Sigma^{-1}$ is also the adjacency matrix of the GGM, indicating which pairs are conditionally dependent. \TODO{discuss how quickly (or slowly) this breaks down with deviations from gaussianity, e.g.~MaxEnt models, Ising models.} \TODO{Also, motivate this from the perpsective of linear regression as in \cite{Varoquaux:2012}.} The off-diagonal elements of $S$ are proportional to partial pairwise correlations between corresponding pairs of neurons. \TODO{Expand.} Regularization of covariance matrix estimation by sparsifying the inverse of the estimate has been using in function genomics \cite{Schafer:2005,other} and fMRI functional connectivity \cite{Varoquaux:2012}.

The covariance matrix estimate is then 
\begin{equation}
-\hat\Sigma_\rho^{-1} =\arg\min\limits_S \loss{-S^{-1},\hat\Sigma_0}  \quad \mbox{such that} \quad  \|S_\rho\|_0 = \rho
\end{equation}
where $S_\rho$ is a sparse matrix with $\rho$ non-zero coefficients. $\|S\|_0$ denotes the number of non-zero elements of matrix $S$.
Solving this approximation in this form is computationally challenging. The problem can be made computationally tractable by replacing the $L_0$ norm with the $L_1$ norm, which converts the problem into one of convex optimization \cite{Donoho:2000}.  The resulting algorithm, known as \emph{graphical lasso} or \emph{GLASSO}  \cite{Meinshausen:2006,Banerjee:2008,Friedman:2008}, produces the following estimator  
\begin{equation}
-\hat\Sigma_\lambda^{-1} = \arg\min\limits_S \loss{-S^{-1},\hat\Sigma_0} + \lambda \|S\|_1
\end{equation}
where $\lambda \|S\|_1$ is the $L_1$ norm of the matrix. \TODO{clarify}.

@@

The inverse $S=-\Sigma^{-1}$ of the covariance matrix of a GGM constitutes the graph of conditional dependencies (interactions) between the units.  With the assumption of sparse organization of interactions in the network, $S$ is assumed to be sparse.  When the observed units are part of a larger GGM that includes other latent units, let the negative inverse $S^*$ of the joint distribution of both observed and latent units be composed of four partitions
\begin{equation}
S^* = 
\begin{pmatrix}
S_{11} & S_{12} \\
S_{12}^\T & S_{22} 
\end{pmatrix}
\end{equation}
where partition $S_{11}$ describes the interactions between the visible units, $S_{12}$ describe the interactions between visible and latent units, and $S_{22}$ describes the interactions between the latent units. 
Then the covariance matrix of between the observed unit is 
\begin{equation}
\Sigma = -\left(S_{11} - S_{12}S_{22}^{-1}S_{12}^\T\right)^{-1}
\end{equation} 
The rank of matrix $S_{12}S_{22}^{-1}S_{12}$ equals the number of latent units. Rather than solving for the precise dependency structure with and between latent units in matrices $S_{12}$ and $S_{22}$, we simply replace the matrix $- S_{12}S_{22}^{-1}S_{12}$ with on low-rank matrix $L_d=- S_{12}S_{22}^{-1}S_{12}$ with rank $d$.

Then we obtain estimator $\hat\Sigma_{d,\rho}$, parameterized by the sparsity parameter $\rho$ and  the number of latent units $d$:
\begin{equation}
\begin{split}
-\hat\Sigma_{d,\rho}^{-1} &= \hat S_\rho + \hat L_d
\\
(\hat S_\rho, \hat L_d) &= \arg\min\limits_{S,L} \loss{-(S+L),\Sigma_0} \quad \mbox{such that} \quad \|S\|_0=\rho \quad \mbox{and} \quad \rank(L) = d
\end{split}
\end{equation}

Again, in this formulation, the problem is computationally intractible.  The problem can be made convex by replacing the $L_0$ norm with $L_1$ norm. The resulting algorith, known as \emph{latent-variable graphical lasso} or \emph{LV-GLASSO} \cite{Chandrasekaran:2010,Ma:2013}, produces estimator $\hat\Sigma_{d,\lambda}$:
\begin{equation}
\begin{split}
-\hat\Sigma_{d,\lambda}^{-1} &= \hat S_\lambda + \hat L_d
\\
(\hat S_\lambda, \hat L_d) &= \arg\min\limits_{S,L} \loss{-(S+L),\Sigma_0} + \lambda \| S \|_1 \quad \mbox{such that}  \quad \rank(L) = d
\end{split}
\end{equation}
